Spectroscopic confirmation of very-wide binaries and large-separation comoving stars from \textsl{Gaia DR1}

### 2017-07-10 paper/comoving-followup.tex
todos

\subsubsection{TYC 2486-1699-1 \& TYC 2477-430-1}

\todo{Highlight a binary sequence-main sequence pair}

\subsubsection{TYC 3792-658-1 \& HD 54318}

\todo{Highlight the largest mag difference MS pair}

@@

Abundances - future work, Coronado in prep.!

>>>>

\subsubsection{HD 151090 \& HIP 81988}

\todo{G-subgiant - K-dwarf - well known high proper-motion comoving pair}

\subsubsection{HD 54318 \& TYC 3792-658-1}

\todo{Highlight the largest mag difference MS pair - K-dwarf - B-star}

@@

Abundances - future work, Coronado in prep.! But: throw shade on abundances
because planet engulfment (https://arxiv.org/pdf/1707.02180.pdf). Also Oh et al.
2017b
